### 2022-12-20 files/Chapter3/dynamicconvergence.tex
added some work on chapter 3

In Section 2.2, a general variational problem Problem GVar from \cite{VV02} is given. The authors of \cite{BV13} use the same general variational problem.

@@

Before we can look at the results of \cite{BV13}, some preparation is required. To start, the authors of \cite{BV13} formulate the Galerkin Approximation of Problem GVar.

@@

@@

Now we look at the main results of \cite{BV13}.
\subsection{Main result}

\newtheorem*{DC_Thm5}{Theorem 2}
\begin{DC_Thm5}
	{Main Result}\\
	If $f\in C^{2}([0,T],X)$, then
	\begin{eqnarray*}
		\Vert u_{h}(t_{k})-u_{k}^{h}\Vert_{W}\ & \leq & 7T^{2}\tau^{2}\max\Vert u_{h}^{(4)}\Vert_{W}+7T\tau^{2}\max\Vert u_{h}'''\Vert_{W}\\
		& & + \sqrt{2K_{a}}\tau^{4}\max\Vert u_{h}'''\Vert_{W}
	\end{eqnarray*}
	for each $t\in(0,\ T)$.
\end{DC_Thm5}

\subsection{Obtaining the error estimate}
In this section we will show how the error estimate in Theorem 2 is obtained in \cite{BV13}.The following two assumptions are made in \cite{BV13}.

\subsubsection*{Assumptions}
\begin{itemize}
	\item[] \textbf{B1} - The solution $u \in C(J,V)$ of Problem GVar$^h$ has the property that $(Pu) \in C^2(J)$.

@@

The projection $P$ in section \eqref{e_est} is defined in \cite{BV13} as
\begin{eqnarray*}
	b(u-P_hu,v) = 0 \ \ \ \textrm{ for all } v \in V.
\end{eqnarray*}

@@

In \cite{BV13}, this is presented as a proposition.
\newtheorem{DC_Prop1}{Proposition}
\begin{DC_Prop1}
	If $u$ is the solution of Problem GVar and $u$ satisfies assumption \textbf{B1}, then

	\begin{eqnarray}
		c(e''(t),v) + a(e'(t),v) + b(e(t),v) = 0 \ \ \ \textrm{ for all } v \in V.
	\end{eqnarray}
\end{DC_Prop1}

>>>>

In Section 2.2, a general variational problem, called Problem GVar, which is identical to the one in \cite{VV02} is given. From this model, a Galerkin Approximation can be derived.

@@

Before the main theory of \cite{BV13} can be discussed, some preparation is required. First the Galerkin approximation is for Problem GVar is derived. Then a equivalent system of ordinary differential equations is derived using the Finite Element Method.\\

@@

This theorem is presented in \cite{BV13}.

@@

\subsection{Main result}

The main result proving the convergence of the solution of the Galerkin Approximation is given in \cite{BV13} as follows.

\newtheorem*{DC_Thm5}{Theorem 2}
\begin{DC_Thm5}
	{Main Result}\\
	If $f\in C^{2}([0,T]4,X)$, then
	\begin{eqnarray*}
		\Vert u_{h}(t_{k})-u_{k}^{h}\Vert_{W}\ & \leq & 7T^{2}\tau^{2}\max\Vert u_{h}^{(4)}\Vert_{W}+7T\tau^{2}\max\Vert u_{h}'''\Vert_{W}\\
		& & + \sqrt{2K_{a}}\tau^{4}\max\Vert u_{h}'''\Vert_{W}
	\end{eqnarray*}
	for each $t\in(0,\ T)$.
\end{DC_Thm5}

The parameter $\tau$ is some number in $(0,T)$. The constant $K_\alpha$ is the constant defined in assumption \textbf{A4} of Section 2.2.1.

\subsection{Obtaining the error estimate}
In this section we will show how the error estimate in Theorem 2 is obtained by the authors of \cite{BV13}.\\

The following two assumptions are made in \cite{BV13}.
\subsubsection*{Assumptions}
\begin{itemize}
	\item[] \textbf{B1} - The solution $u \in C(J,V)$ of Problem GVar$^h$ has the property that $(Pu) \in C^2(J)$.

@@

The projection $P$ in section \eqref{e_est} is defined in \cite{BV13} as
\begin{eqnarray*}
	b(u-Pu,v) = 0 \ \ \ \textrm{ for all } v \in V.
\end{eqnarray*}

@@

In \cite{BV13}, this is presented as a proposition.
\newtheorem{DC_Prop1}{Proposition}
\begin{DC_Prop1}
	If $u$ is the solution of Problem GVar and $u$ satisfies assumption \textbf{B1}, then
	\begin{eqnarray}
		c(e''(t),v) + a(e'(t),v) + b(e(t),v) = 0 \ \ \ \textrm{ for all } v \in V.
	\end{eqnarray}
\end{DC_Prop1}
